\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A Guide for International Students

### 2023-09-17 demystify.tex
Updates from Overleaf
update

So I want to share some details about the PhD admission process and advice for those who are interested in applying for a \textbf{PhD in Computer Science in the US}.
While this document is primarily intended for students interested in CS, it may be relevant to students from various disciplines.
Furthermore, although many examples are specifics for George Mason University, the information should be generalizable to other R1\footnote{An \href{https://en.wikipedia.org/wiki/List_of_research_universities_in_the_United_States}{R1 institution} in the US is a research-intensive university with a high level of research activity across various disciplines.} institutions in the US  (though \emph{very} top schools could be very selective, e.g., see the \href{https://da-data.blogspot.com/2015/03/reflecting-on-cs-graduate-admissions.html}{admission process} at CMU).

@@

@@

\bibliographystyle{abbrv}
\bibliography{phd-cs-us.bib}

>>>>

So I want to share some details about the PhD admission process and advice for those who are interested in applying for a \textbf{PhD in Computer Science in the US}.
While this document is primarily intended for students interested in CS, it may be relevant to students from various disciplines.
Furthermore, although many examples are specifics for George Mason University (GMU), the information should be generalizable to other R1\footnote{An \href{https://en.wikipedia.org/wiki/List_of_research_universities_in_the_United_States}{R1 institution} in the US is a research-intensive university with a high level of research activity across various disciplines.} institutions in the US  (though \emph{very} top schools could be very selective, e.g., see the \href{https://da-data.blogspot.com/2015/03/reflecting-on-cs-graduate-admissions.html}{admission process} at CMU).

@@

\section{Cultural Differences and Tips}

This section lists various things related to studying the US that I notice international students often get surprised or confused.

\begin{enumerate}
    \item \textbf{Cheating}: Cheating, e.g., exams, coding, is a big no-no in the US.  If you're caught cheating, you will face very heavy consequence and likely be expelled from the university (e.g., after the second time).   This is very different from many international countries where cheating is common and often tolerated.  Faculty is extremely good at detecting cheating (how would we not?  we have deal with these situations so many times over so many years), and \emph{will} report cheating cases.  In short, whatever you do, don't cheat---not worth it.
    \item \textbf{Illegal Software}: Using illegal/cracked software is very common in many countries. But do not use/install them on university computer (e.g., computers given by your department or advisor).  It is unlikely that the university will track you down, but it is the \textbf{software company} that will.  They have very sophisticated tools to detect illegal software and will sue your university/department (imagine your department or advisor being sued for half a million dollars, and it is you who caused it).   If you need software, ask your advisor or the department.
\end{enumerate}

@@

\bibliographystyle{abbrv}
\bibliography{demystify.bib}
